Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2021-02-12 bbbq_article.tex
Clean up article, use 14-mers

It is important that MHC-I presents both the peptides of the 
(healthy) cell, as well as possible pathogen-derived peptides when the
cell is infected. As described above, MHC-I presents TMH-derived epitopes 
from the human host more often. It is unknown if MHC-I has the same
dedication to present epitopes that stem from TMHs derived from
proteins produced by pathogen, either would the pathogen
be a virus \richel{$\mathcal{H}_{1,1}$} or 
a bacterium \richel{$\mathcal{H}_{1,2}$}.

@@

It is unknown if MHC-II, like MHC-I, 
presents TMH-derived epitopes as often, either 
in humans \richel{$\mathcal{H}_{2,1}$},
bacteria \richel{$\mathcal{H}_{2,2}$}
or viruses \richel{$\mathcal{H}_{2,3}$}.

@@

The 13 MHC-I haplotypes used in this study are the same as 
the ones in \cite{bianchi2017}.
The MHC-II haplotypes used additionally are selected 
to occur with a phenotypic frequency of at least 
\richel{recalculate number}
14\% in
the human population (\cite{greenbaum2011functional},
see \ref{table:mhc2_haplotypes} for coverage),
resulting in 21 haplotypes.
When using an MHC-II haplotype, instead of using 9-mers, 13-mers are
used, as these are the canonical MHC-II epitope size \richel{Reference here}.

Where the original study used a significance level of 1\% 
for the binomial test to determine if TMH-derived peptides 
are as likely to be a binder as expected by chance, this study
uses 5\%, which is a common significance level for an exploratory study.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Comparing amounts of TMH epitopes}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

To determine if MHC-I has the same percentage of epitopes overlapping
with viral/bacterial TMHs as with human TMHs \richel{$\mathcal{H}_{1,VB}$}, 
we compare the distributions of the measured percentages 
of TMH-overlapping peptides for all haplotypes,
and compare the distributions between humans and each pathogen
using a two-sample Kolmogorov-Smirnov (KS) test
for a significance level $\alpha = 0.05$, 
which is a common significance level for an exploratory study.

>>>>

It is important that MHC-I presents both the peptides of the 
(healthy) cell, as well as possible pathogen-derived peptides when the
cell is infected. As described above, MHC-I presents TMH-derived epitopes 
from the human host more often. It is unknown if MHC-I has the same
dedication to present epitopes that stem from TMHs derived from
proteins produced by pathogen, either would the pathogen
be a virus or 
a bacterium.

@@

It is unknown if MHC-II, like MHC-I, 
presents TMH-derived epitopes as often, either 
in humans,
bacteria or viruses.

@@

The 13 MHC-I haplotypes used in this study are the same as 
the ones in \cite{bianchi2017}.
The MHC-II haplotypes used additionally are selected 
to occur with a phenotypic frequency of at least 14\% in
the human population (\cite{greenbaum2011functional},
see \ref{table:mhc2_haplotypes} for coverage),
resulting in 21 haplotypes.
When using an MHC-II haplotype, instead of using 9-mers, 14-mers are
used, as these are the most common MHC-II epitope size,
as found in the elution study (\cite{bergseng2015different}).
